Fourmile Calibrations and Output

### 2024-06-14 38HRU_model/fourmile_model_outputs.Rmd
added in burned vs unburned param boxplots
updating git ignore

@@

@@

gw_grid <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid')

gw_statn <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn')

gw <- bind_rows(gw_grid, gw_statn) %>%
  mutate(year = year(time)) %>%
  rename(date = time)

@@

gw <- gw %>%
  group_by(year, source) %>%
  mutate(RD1cumsum = cumsum(catchmentRD1_w),
         RD2cumsum = cumsum(catchmentRD2_w),
         RG1cumsum = cumsum(catchmentRG1_w),
         RG2cumsum = cumsum(catchmentRG2_w))

@@

gw_maxcumsum <- gw %>%
  group_by(source, year) %>%
  summarize(yr_max_RD1 = max(RD1cumsum),
            yr_max_RD2 = max(RD2cumsum),
            yr_max_RG1 = max(RG1cumsum),
            yr_max_RG2 = max(RG2cumsum)) %>%
  mutate(year = as.factor(year)) %>%
  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms')

@@

>>>>

# find min and max of grid and statn param for sensitivity analysis
# grid_minmax <- grid %>%
#   group_by(param) %>%
#   summarize(min = as.numeric(min(value)),
#             max = as.numeric(max(value))) %>%
#   mutate(input = 'grid_unburn')
# 
# statn_minmax <- statn %>%
#   group_by(param) %>%
#   summarize(min = as.numeric(min(value)),
#             max = as.numeric(max(value))) %>%
#   mutate(input = 'statn_unburn')
# 
# minmax_burn <- burn_params %>%
#   group_by(params, input_data) %>%
#   summarize(min = min(value),
#             max = max(value)) %>%
#   mutate(input = paste(input_data, '_burn')) %>%
#   dplyr::select(-input_data) %>%
#   rename(param = params) %>%
#   mutate(param = as.character(param))
# 
# minmax_params <- bind_rows(grid_minmax, statn_minmax, minmax_burn)
# write.csv(minmax_params, 'min_max_params.csv')

@@

# boxplots of burned and unburned

ggplot(params_combo, aes(x=burn, y=value, fill=input_data)) +
  geom_boxplot() +
  facet_wrap(~param, scales = 'free_y')

@@

gw_gridall <- read_csv(here('catchment_output/gridall_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_all')

gw_statnall <- read_csv(here('catchment_output/statnall_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_all')

gw_grid2011 <- read_csv(here('catchment_output/grid2011_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2011')

gw_grid2012 <- read_csv(here('catchment_output/grid2012_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2012')

gw_grid2013 <- read_csv(here('catchment_output/grid2013_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2013')

gw_grid2014 <- read_csv(here('catchment_output/grid2014_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2014')

gw_grid2015 <- read_csv(here('catchment_output/grid2015_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2015')

gw_grid2016 <- read_csv(here('catchment_output/grid2016_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2016')

gw_grid2017 <- read_csv(here('catchment_output/grid2017_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2017')

gw_grid2018 <- read_csv(here('catchment_output/grid2018_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2018')

gw_grid2019 <- read_csv(here('catchment_output/grid2019_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2019')

gw_grid2020 <- read_csv(here('catchment_output/grid2020_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'grid_2020')

gw_statn2011 <- read_csv(here('catchment_output/statn2011_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2011')

gw_statn2012 <- read_csv(here('catchment_output/statn2012_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2012')

gw_statn2013 <- read_csv(here('catchment_output/statn2013_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2013')

gw_statn2014 <- read_csv(here('catchment_output/statn2014_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2014')

gw_statn2015 <- read_csv(here('catchment_output/statn2015_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2015')

gw_statn2016 <- read_csv(here('catchment_output/statn2016_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2016')

gw_statn2017 <- read_csv(here('catchment_output/statn2017_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2017')

gw_statn2018 <- read_csv(here('catchment_output/statn2018_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2018')

gw_statn2019 <- read_csv(here('catchment_output/statn2019_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2019')

gw_statn2020 <- read_csv(here('catchment_output/statn2020_outlet.csv')) %>%
  dplyr::select(time, catchmentRD1_w, catchmentRD2_w, catchmentRG1_w, catchmentRG2_w) %>%
  mutate(source = 'statn_2020')

gw <- bind_rows(
  gw_gridall, gw_statnall,
  gw_grid2011, gw_grid2012,
  gw_grid2013, gw_grid2014,
  gw_grid2015, gw_grid2016,
  gw_grid2017, gw_grid2018,
  gw_grid2019, gw_grid2020,
  gw_statn2011, gw_statn2012,
  gw_statn2013, gw_statn2014,
  gw_statn2015, gw_statn2016,
  gw_statn2017, gw_statn2018,
  gw_statn2019, gw_statn2020
) %>%
  mutate(date = mdy(time),
         year = year(date))

@@

gw <- gw %>%
  arrange(date) %>%
  group_by(year, source) %>%
  mutate(RD1cumsum = cumsum(catchmentRD1_w),
         RD2cumsum = cumsum(catchmentRD2_w),
         RG1cumsum = cumsum(catchmentRG1_w),
         RG2cumsum = cumsum(catchmentRG2_w))

@@

gw_maxcumsum <- gw %>%
  group_by(source, year) %>%
  summarize(yr_cum_RD1 = max(RD1cumsum),
            yr_cum_RD2 = max(RD2cumsum),
            yr_cum_RG1 = max(RG1cumsum),
            yr_cum_RG2 = max(RG2cumsum)) %>%
  mutate(year = as.factor(year)) %>%
  pivot_longer(!c(year, source), names_to = 'flow_type', values_to = 'flow_cms')

@@

# Join param & RD/RG

join <- gw_maxcumsum %>%
  rename(input_data = source)

params1 <- params %>%
  dplyr::select(-input_data) %>%
  rename(input_data = cal) %>%
  dplyr::select(-c(year_missing))

join <- left_join(join, params1, by = c('input_data')) %>%
  pivot_wider(., names_from='param', values_from='value') %>%
  pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms')

write_csv(join, 'flow_params.csv')
